\normalfont{A bird's-eye view on the habitability of exoplanets via statistical learning techniques}

### 2020-09-23 Manuscript/Manuscript.tex
PUB

\documentclass[
12pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
%twoside, % Two page layout (page indentation for binding and different headers)
headinclude,footinclude, % Extra spacing for the header and footer
BCOR5mm, % Binding correction
]{scrartcl}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage{titlepic}
\usepackage{epigraph}
\usepackage{mathcomp}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{url}
\usepackage{sectsty}
\usepackage[dvipsnames,table,xcdraw,svgnames]{xcolor}
\usepackage{listings}
\usepackage{url}
\lstset{language=R,
    basicstyle=\small\ttfamily,
    stringstyle=\color{DarkGreen},
    otherkeywords={0,1,2,3,4,5,6,7,8,9},
    morekeywords={TRUE,FALSE},
    deletekeywords={data,frame,length,as,character},
    keywordstyle=\color{blue},
    commentstyle=\color{DarkGreen},
}

@@

>>>>

\documentclass[
12pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
%twoside, % Two page layout (page indentation for binding and different headers)
headinclude,footinclude, % Extra spacing for the header and footer
BCOR5mm, % Binding correction
]{scrartcl}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage{titlepic}
\usepackage{epigraph}
\usepackage{mathcomp}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{url}
\usepackage{sectsty}
\usepackage[dvipsnames,table,xcdraw,svgnames]{xcolor}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{url}
\lstset{language=R,
    basicstyle=\small\ttfamily,
    stringstyle=\color{DarkGreen},
    otherkeywords={0,1,2,3,4,5,6,7,8,9},
    morekeywords={TRUE,FALSE},
    deletekeywords={data,frame,length,as,character},
    keywordstyle=\color{blue},
    commentstyle=\color{DarkGreen},
}

@@

\begin{table}[]
\begin{tabular}{@{}lll@{}}
\cmidrule(r){1-3}
Variable name & Abbreviation & Description                                                                                          \\ \cmidrule(r){1-3}
Planet name   & P\_NAME      & \begin{tabular}[c]{@{}l@{}}The planet name according to \\ the international convention\end{tabular} \\
              &              &                                                                                                      \\
              &              &                                                                                                      \\
              &              &                                                                                                      \\
              &              &                                                                                                      \\
              &              &                                                                                                      \\
              &              &                                                                                                      \\
              &              &                                                                                                      \\
              &              &                                                                                                      \\
              &              &                                                                                                      \\
              &              &                                                                                                      \\
              &              &                                                                                                      \\
              &              &                                                                                                      \\
              &              &                                                                                                      \\ \cmidrule(r){1-3}
\end{tabular}
\end{table}
